---
title: "R Notebook"
output: html_notebook
---

Here will be working with salt and temperature experiment talk about this experiment

Keep in mind that we are screening for NaCL (salt) and high temperature tolerance


Packages and dependencies
```{r}
#install.packages("ggplot2")
library(ggplot2)
#install.packages("tidyverse")
library(tidyverse)
library(phyloseq)
#install.packages("ggpubr")
library(ggpubr)
#install.packages("lsmeans")
library(lsmeans)
#install.packages("emmeans")
library(emmeans)
library(lme4)
#install.packages("multcomp")
library(multcomp)
```

Palettes
```{r}
cbbPalette <- c("#000000", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
```

Load dataset
```{r}
temperature_experiment <- read.csv("/Users/lau/Desktop/AU_research/Old_Rotation/August.2021/Salt_Experiment/temperature_Experiment/2022/2023/2023.03.24temperature_experiment31+23\ copy.csv", na.strings = "na")
str(temperature_experiment)
```

First thing we are doing is visualizig all the screnned isolates that grew at least a bit in high NaCl and at the two different temepratures
```{r}
ggplot(na.omit(temperature_experiment), aes(x = Hours, y = MM, color = interaction(Conc, Temperature))) +
  stat_summary(fun.y=mean,geom="line", width = 0.95) +
  stat_summary(fun.data = mean_se, geom = "errorbar", width = 0.70) +
  ylab("Millimeters") +
  xlab("")+
  scale_color_manual(values=c(cbbPalette)) +
  theme_classic() +
 facet_wrap(~Isolate*Species, scales = "free")
```

Based on upper result we decided to work with isolates P. citrinum since it seems the high salt and high temperatures make the fungus grow better
So, here we subset for P. citrinum and the Mortierellas and Linnemannia (becuse of known plant growth promotion)
```{r}
#Subset
temperature_experiment_sub <- temperature_experiment %>%
  subset(Isolate %in% c("CCH_F37_B", "OEO-196", "OEO-198", "OEO-304", "OEO-305"))

q <- ggplot(na.omit(temperature_experiment_sub), aes(x = Hours, y = MM, color = interaction(Conc, Temperature))) +
  stat_summary(fun.y=mean,geom="line", width = 0.95) +
  stat_summary(fun.data = mean_se, geom = "errorbar", width = 0.70) +
  ylab("Millimeters") +
  xlab("Time (hours)")+
  scale_color_manual(values=c(cbbPalette)) +
  theme_classic() +
  facet_wrap(~Isolate*Species, scales = "free")
q + theme(axis.text.x = element_text(angle = 60, hjust = 1))

```
Linear model analysis for salt for P. citrinum and Mortierellas/Linnemannia
First subset for the treatment I was interested in and then did a linear model that tested the ASK MORGAN HOW TO DESCRIBE
```{r}
citrinum <- temperature_experiment %>%
  subset(Isolate %in% c("CCH_F37_B"))
  
lm.citrinum <- lm(Growth_rate~ as.factor(Conc) + Temperature + as.factor(Conc)*Temperature, data = citrinum)
summary(lm.salt)
anova(lm.salt)
```

Same thing but for M. calciphila OEO-304
```{r}
calciphila <- temperature_experiment %>%
  subset(Isolate %in% c("OEO-304"))
  
lm.calciphila <- lm(Growth_rate~ as.factor(Conc) + Temperature + as.factor(Conc)*Temperature, data = citrinum)
summary(lm.salt)
anova(lm.salt)
```




















