---
title: "R Notebook"
output: html_notebook
---

Here will be screening salt and temperature to test for a tolerant fungi to these factors

Packages and dependencies
```{r}
#install.packages("ggplot2")
library(ggplot2)
#install.packages("tidyverse")
library(tidyverse)
library(phyloseq)
#install.packages("ggpubr")
library(ggpubr)
#install.packages("lsmeans")
library(lsmeans)
#install.packages("emmeans")
library(emmeans)
library(lme4)
#install.packages("multcomp")
library(multcomp)
```

Palettes
```{r}
cbbPalette <- c("#000000", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
```

Load data set
```{r}
temperature_experiment <- read.csv("/Users/lau/Desktop/AU_research/Old_Rotation/Jan2022/PGPFpeanut/Data/01_TemperatureSaltExp.csv", na.strings = "na")
str(temperature_experiment)
```

First thing we are doing is visualizing all the screened isolates that grew at least a bit in high NaCl and at the two different temperatures
```{r}
ggplot(na.omit(temperature_experiment), aes(x = Hours, y = MM, color = interaction(Conc, Temperature))) +
  stat_summary(fun.y=mean,geom="line", width = 0.95) +
  stat_summary(fun.data = mean_se, geom = "errorbar", width = 0.70) +
  ylab("Millimeters") +
  xlab("")+
  scale_color_manual(values=c(cbbPalette)) +
  theme_classic() +
 facet_wrap(~Isolate*Species, scales = "free")
```

Based on upper result we decided to work with isolates P. citrinum since its growing at high NaCl and high temperature
So, here we subset for P. citrinum and the Mortierella and Linnemannia (because of known plant growth promotion)
```{r}
#Subset
temperature_experiment_sub <- temperature_experiment %>%
  subset(Isolate %in% c("CCH_F37_B", "OEO-196", "OEO-198", "OEO-304", "OEO-305"))

q <- ggplot(na.omit(temperature_experiment_sub), aes(x = Hours, y = MM, color = interaction(Conc, Temperature))) +
  stat_summary(fun.y=mean,geom="line", width = 0.95) +
  stat_summary(fun.data = mean_se, geom = "errorbar", width = 0.70) +
  ylab("Millimeters") +
  xlab("Time (hours)")+
  scale_color_manual(values=c(cbbPalette)) +
  theme_classic() +
  facet_wrap(~Isolate*Species, scales = "free")
q + theme(axis.text.x = element_text(angle = 60, hjust = 1))

```
Linear model analysis for salt for P. citrinum and Mortierellas/Linnemannia
First subset for the treatment I was interested in and then did a linear model that tested if the growth was positielly or negativelly altered due to high temperatures or salinity.
```{r}
citrinum <- temperature_experiment %>%
  subset(Isolate %in% c("CCH_F37_B"))
  
lm.citrinum <- lm(Growth_rate~ as.factor(Conc) + Temperature + as.factor(Conc)*Temperature, data = citrinum)
summary(lm.salt)
anova(lm.salt)
```

Same thing but for M. calciphila OEO-304
```{r}
calciphila <- temperature_experiment %>%
  subset(Isolate %in% c("OEO-304"))
  
lm.calciphila <- lm(Growth_rate~ as.factor(Conc) + Temperature + as.factor(Conc)*Temperature, data = citrinum)
summary(lm.salt)
anova(lm.salt)
```

