---
title: "R Notebook"
output: html_notebook
---

Growth chamber well water experimen. Peanut were inoculated with five different fungal isolates from Alabama cotton fields (Mortierellas and Linnemannia) and from the Old Rotation (P. citrinum)

here we analyze and visualize the growth chamber results (Phi2, shoot and root biomass)

Loading Packages and dependencies
```{r}
library(ggplot2)
library(tidyverse)
library(ggpubr)
library(emmeans)
library(multcomp)
library(lsmeans)
library(lme4)
library("lmerTest")
```

Palettes 
```{r}
cbbPalette <- c("#000000", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
fungi.colors <- c("#c6dbef","#9ecae1","#6baed6","#3182bd","#08519c",
                           "#c7e9c0", "#a1d99b", "#74c476", "#41ab5d", "#238b45", "#005a32",
                           "#fdd0a2", "#fdae6b", "#fd8d3c", "#f16913", "#d94801", "#8c2d04",
                           "#dadaeb", "#bcbddc", "#9e9ac8", "#807dba", "#6a51a3", "#4a1486",
                           "#fcbba1", "#fc9272", "#fb6a4a", "#ef3b2c", "#cb181d", "#99000d",
                           "#d9d9d9", "#bdbdbd", "#969696", "#737373", "#525252", "#252525")
```

Loading dataset
```{r}
photosynq <- read.csv("/Users/lau/Desktop/AU_research/Old_Rotation/Jan2022/Growthchamberexp/02.19.2023wellwaterGC/2023.04.05GrowthchamberWellH2Ophotosynq.csv", na.strings = "null")

str(photosynq)

```


We decided to exclude treatment NVP5.
```{r}
photosynq_sub <-  photosynq %>%
  subset(!Treatment %in% c("NVP5"))
```

Let's first analyze and visualize the shoot biomass data
We used the linear model to test the effect of the treatments (fungal inoculations) in the shoot dry biomass of the peanuts. With this we tested one-way ANOVA to test the differences of means of the treatments and we lsmeeans we got the p-value btw treatments
```{r}
lm.shoot <- lm(Shootbiomass~ Treatment, data = photosynq_sub)
#plot(lm.shoot)
summary(lm.shoot)
anova(lm.shoot)
lsmeans.shoot <- emmeans(lm.shoot, ~ Treatment, adjust = "tukey") # estimate lsmeans

Results_lsmeeans <- cld(object = lsmeans.shoot,
                        Letters = letters, reversed = TRUE, details = TRUE) # contrast with Tukey ajustment
```
Graph
```{r}
#graph
shootbiomass <- photosynq_sub %>%
  ggplot(aes(x = Treatment, y = 1000*Shootbiomass)) +
  stat_summary(fun.y=mean,geom="bar", width = 0.75, position = "dodge") +
  stat_summary(fun.data = mean_se, geom = "errorbar", width = 0.5, position = "dodge") +
  geom_jitter()+
  #keep and aye for this command; it only substitute the label it does not means that is the correct label for the bar.
  scale_x_discrete(labels = c("P. citrinum CCH_F37_B", "Control", "L. elongata OEO-196",
                              "L. elongata OEO-198", "M. calciphila OEO-304", "M. alpina OEO-305")) +
  ylab("Shoot biomass (mg)") +
  xlab("") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 60, vjust = 1, hjust=1))

```


Root biomass
```{r}
lm.root <- lm(Rootbiomass~ Treatment, data = photosynq_sub)
#plot(lm.root)
summary(lm.root)
anova(lm.root)
lsmeans.root <- emmeans(lm.root, ~ Treatment, adjust = "tukey") # estimate lsmeans

Results_lsmeeans <- cld(object = lsmeans.root,
                        Letters = letters, reversed = TRUE, details = TRUE) # contrast with Tukey ajustment
```
graph
```{r}
rootbiomass <- photosynq_sub %>%
  #subset(dayspostdrought == 12) %>%
  ggplot(aes(x = Treatment, y = 1000*Rootbiomass)) +
  stat_summary(fun.y=mean,geom="bar", width = 0.75, position = "dodge") +
  stat_summary(fun.data = mean_se, geom = "errorbar", width = 0.5, position = "dodge") +
  geom_jitter()+
  ##keep and aye for this command; it only substitute the label it does not means that is the correct label for the bar.
  scale_x_discrete(labels = c("P. citrinum CCH_F37_B", "Control", "L. elongata OEO-196",
                              "L. elongata OEO-198", "M. calciphila OEO-304", "M. alpina OEO-305")) +
  ylab("Root biomass (mg)") +
  xlab("") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 60, vjust = 1, hjust=1))
```

Want to make it pretty? well let's put both root and shoot fig. together with ggarrange and label them as a) and b) for writing purposes 
```{r}
ggarrange(shootbiomass, rootbiomass, labels = c("a", "b"))
```

Now let's look at the Phi2. Phi2 measures the amount of incoming light that the plant uses for photosynthesis.
Here we analyzed the light used for photosynthesis (Phi2) against the days post drought since these measurements were taken throughout the experiment.
For the visualization we selected only a few time points
```{r}
lm.phi2 <- lm(Phi2~ Treatment*as.factor(dayspostdrought), data = photosynq_sub)
#plot(lm.)
summary(lm.phi2)
#modified to obtain the pvalue
car::Anova(lm.phi2, test.statistic = "F")
anova(lm.phi2)
lsmeans.phi2 <- emmeans(lm.phi2, ~ Treatment|dayspostdrought, adjust = "tukey") # estimate lsmeans

Results_lsmeeans <- cld(object = lsmeans.phi2,
                        Letters = letters, reversed = TRUE, details = TRUE) # contrast with Tukey ajustment

#Graph
photosynq_sub %>%
  subset(dayspostdrought %in% c(6:12)) %>%
  ggplot(aes(x = Species, y = Phi2, fill = Species)) +
  stat_summary(fun.y=mean,geom="bar", width = 0.75, position = "dodge") +
  stat_summary(fun.data = mean_se, geom = "errorbar", width = 0.5, position = "dodge") +
  scale_fill_manual(values=fungi.colors) +
  ##keep and aye for this command; it only substitute the label it does not means that is the correct label for the bar.
  scale_x_discrete(labels = c("Control", "L. elongata OEO-196", "L. elongata OEO-198",
                              "M. alpina OEO-305", "M. calciphila OEO-304","P. citrinum CCH_F37_B")) +
  ylab("Phi2") +
  xlab("") +
  facet_wrap(~dayspostdrought)+
  theme_classic() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```



































































































































































